A Bayesian Framework for Learning Regular Expressions

### 2012-12-09 paper/paper.tex
edited discussion status

We note that in cases 16 (S = \{`yyyt', `yt', `yyyt', `yyyt', `yt'\}, s= `yyyyyt'), 17 (S = \{`jojojojo', `jojojojo', `jojojojo'\}, s = `jojo'), and 18 (S = \{`twtwtw', `twtwtw', `twtwtw'\}, s =  `tw'), it is clear that the model weighs a smaller number of transitions greater than human subjects do far more than humans do as a result of our beta term. Here, the prior on the hypothesis is so low that the difference in the likelihood of the base hypothesis as compared to a hypothesis with fewer states and more loops that the posterior probability becomes relatively unlikely. Future work could better determine how this term should be set. However, because this same parameter in part controls for wildcards, lowering it reduces performance on many other cases.

>>>>

We note that in cases 16 (S = \{`yyyt', `yt', `yyyt', `yyyt', `yt'\}, s= `yyyyyt'), 17 (S = \{`jojojojo', `jojojojo', `jojojojo'\}, s = `jojo'), and 18 (S = \{`twtwtw', `twtwtw', `twtwtw'\}, s =  `tw'), it is clear that the model favors a smaller number of transitions far more than humans do as a result of our beta term. Here, the prior on the hypothesis is so low that the difference in the likelihood of the base hypothesis as compared to a hypothesis with fewer states and more loops that the posterior probability becomes relatively unlikely. Future work could better determine how this term should be set. However, because this same parameter in part controls for wildcards, lowering it reduces performance on many other cases.
